%Task VI: Plan deployment
\chapter{Plan deployment}
Due to our evaluation we group our plan deployment in following four sections:
\begin{enumerate}
	\item Modules and Components
	\item Countries
	\item Operating System
	\item Effort
\end{enumerate}

\section{Modules and Components}
Our model explains us, that the module Ads and the components C7 and C6 are high likely to increase the probability for a major fault. Therefore in the planning phase of future projects we should if possible try to avoid or substitute these factors. Another way is to include internal or external experts during the development process for the problematic modules and components to our project team. In general it would be helpful to offer more trainings for these problems to our employees. Also we should analyse and refactor the concerning implementations in our continuous improvement process. Another possibility is to try to substitute these modules and components by different products or providers.

\section{Countries} 
The model showed that most of our developer teams in the countries do not influence the amount of major faults. But it should be a general aim to improve our developer teams. For that reason we should offer more training classes. This seems to be the most important for our teams in Portugal. Maybe the experts in Italy can support the teams of other countries in complex projects. That teams can benefit from the Italian knowledge.

\section{Operating System}
In this section it is not mandatory to introduce actions and processes, because the operating systems do not cause much trouble to our software. Although it would not harm to analyse and refactor our implementations for MAC and enhance our knowledge through trainings and experts.

\section{Effort}
More complex projects should be split to more smaller projects to reduce the probability of major faults. This could be realized in planning phase of the project.

\section{Measurement}
For monitoring it is necessary to frequently evaluate new projects to check if these variables are still critical factors for major incidents and evaluate the success of our actions. This can happen on a yearly base. The success can be measured by the new amount in percentage of our major faults. Furthermore it can be evaluated by the occurring support events, customer satisfaction, sold products and the gained new customers. Therefore the company should earn more money and reduce the bug fixing costs.
